Code for Graphs for ASN presentation

### 2020-12-21 ASNCode.Rmd
New dataset, adjusted axis title

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedDec14final.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

@@

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
  theme_bw() + 
  geom_smooth(method = "lm", se = F) +
  geom_point(alpha = 0.8, aes(shape = food)) + 
  scale_shape_manual(values = c(19, 6)) +
  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
  labs(x = "Number of wasps emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
       color = "Heat Shock Status")
```

>>>>

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedDec19final.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

@@

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
  theme_bw() + 
  ylim(0, 1.05) + 
  geom_smooth(method = "lm", se = F) +
  geom_point(alpha = 0.8, aes(shape = food)) + 
  scale_shape_manual(values = c(19, 6)) +
  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
  labs(x = "Number emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
       color = "Heat Shock Status")
```
